### 2016-06-23 testbed_http.tex
Major push on http image and image fixes

Mount http root and home directories
\begin{lstlisting}[]
$ export HTTPROOTDIR="${WORKDIR}/httproot"
$ mkdir -p ${HTTPROOTDIR}
# mount ${HTTPROOTIMAGE}.img ${HTTPROOTDIR}
# mount ${HTTPBOOTIMAGE}.img ${HTTPROOTDIR}/boot
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

@@

# Parse additional command line options
for x in ${cat /proc/cmdline}; do
    case $x in
    image=*)
        IMAGE=${x#image=}
        # Extract device and path
        # E.g. /dev/mmcblkp2:/root.img --> /dev/mmcblkp2 and /imagedir/root.img
        IMAGEDEV=${IMAGE%:*}
        IMAGEPATH="/imagedir/${${IMAGE#*:}#/}"
        ;;
    url=*)
        URL=${${x#url=}%/}  # If url has trailing slash, then remove it
        ;;
done

@@

    # Mount root as readonly
    losetup /dev/loop0 $(readlink -f ${IMAGEPATH})
    mount -r -n -t ext4 -o nodiratime,noatime /dev/loop0 /root
}

mountroot()
{
    http_mount_root
}

\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

Add the below to \$\{HTTPROOTDIR\}/boot/cmdline.txt (CHANGE URL HERE) (remove init=/usr/lib/raspi-config/init\_resize.sh earlier in guide)
\begin{lstlisting}[]
init=http ro ip=dhcp image=/dev/mmcblk0p2:/root.img root=/dev/loop0 url=http://192.168.87.106/raspi/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
% ip=dhcp root=/dev/http http-options=hard,intr,ro

Edit fstab to look like this (exclude the last line if persistent
home storage directory is not desired):
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{HTTPROOTDIR\}/etc/fstab}@>
<@\textcolor{gray}{
---------------------------------------------------------------}
\Reactivatenumber @>
proc            /proc           proc    defaults          0       0
/dev/mmcblk0p1  /boot           vfat    defaults          0       2
/dev/loop0      /               ext4    defaults,noatime  0       1
/dev/mmcblk0p2  /home           ext4    defaults,noatime  0       1
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

@@

\begin{lstlisting}[]
<@\Suppressnumber @># (echo o;                                      # Create DOS partition table
    echo n; echo p; echo 1; echo ; echo +64M;   # Create boot partition
    echo t; echo b;                             # Set boot partition type to FAT
    echo n; echo p; echo 2; echo ; echo ;       # Create home partition
    echo w                                      # Write table to disk
    ) | sudo fdisk ${HTTPDEV} <@\Reactivatenumber @>
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

%Mount image:
%\begin{lstlisting}[]
%# export DEV=$(sudo losetup --show -f -P ${IMAGE}.img); echo $DEV
%# mount ${DEV}p2 ${ROOTDIR}
%# mount ${DEV}p1 ${ROOTDIR}/boot
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}

Copy boot directory:
\begin{lstlisting}[]
# cp -r ${ROOTDIR}/boot/* ${HTTPBOOTDIR}/ 
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Prepare home directory (Maybe it is better just to copy the content in home from the
image's root partition):
\begin{lstlisting}[]
# install -d -o 1000 -g 1000 -m 700 ${HOMEDIR}/pi && sync
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\begin{lstlisting}[]
# mount ${HTTPDEV}p1 ${HTTPROOTDIR}/boot
# mount ${HTTPDEV}p2 ${HTTPROOTDIR}/home
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Unmount directories:
\begin{lstlisting}[]
# umount ${HTTPBOOTDIR} ${HTTPHOMEDIR}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

>>>>

Mount http root and home directories (ADD LOOP OPTION HERE WHEN MOUNTING)
\begin{lstlisting}[]
$ export HTTPROOTDIR="${WORKDIR}/httproot"
$ mkdir -p ${HTTPROOTDIR}
# mount ${HTTPROOTIMAGE}.img ${HTTPROOTDIR}
# mount ${HTTPBOOTIMAGE}.img ${HTTPROOTDIR}/boot
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

#. /scripts/functions # Already loaded in the init script

@@

# Parse additional command line options
for x in $(cat /proc/cmdline); do
    case $x in
    image=*)
        IMAGE=${x#image=}
        # Extract device and path
        # E.g. /dev/mmcblkp2:/root.img --> /dev/mmcblkp2 and /imagedir/root.img
        IMAGEDEV=${IMAGE%:*}
        IMAGEPATH="${IMAGE#*:}"
        IMAGEPATH="/imagedir/${IMAGEPATH#/}"
        ;;
    url=*)
        URL=${x#url=}
        URL=${URL%/}  # If url has trailing slash, then remove it
        ;;
    esac
done

@@

    # Mount root as readonly
    losetup /dev/loop0 $(readlink -f ${IMAGEPATH})
    mount -r -n -t ext4 -o nodiratime,noatime /dev/loop0 /root

    # Bind /root/home to /home
    #mount -n -o rbind /home /root/home
}

mountroot()
{
    http_mount_root
}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

Add the below to \$\{HTTPROOTDIR\}/boot/cmdline.txt (CHANGE URL HERE) (remove init=/usr/lib/raspi-config/init\_resize.sh earlier in guide)
\begin{lstlisting}[]
boot=http ro ip=dhcp image=/dev/mmcblk0p2:/root.img root=/dev/loop0 url=http://192.168.87.106/raspi/
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
% ip=dhcp root=/dev/http http-options=hard,intr,ro

Edit fstab to look like this (exclude the last line if persistent
home storage directory is not desired):
\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{HTTPROOTDIR\}/etc/fstab}@>
<@\textcolor{gray}{
---------------------------------------------------------------}
\Reactivatenumber @>
proc            /proc           proc    defaults          0       0
/dev/mmcblk0p1  /boot           vfat    defaults          0       2
/dev/loop0      /               ext4    defaults,noatime  0       1
/dev/mmcblk0p2  /home           ext4    defaults,noatime  0       0
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

Unmount:
\begin{lstlisting}[]
# umount ${HTTPROOTIMAGE}/{dev/pts,proc,sys,dev}  
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\subsubsection{Prepare sd-card}

@@

MAYBE ALSO SET THE BOOT FLAG FOR FIRST PARTITION. ALSO UPDATE SCRIPT IF THIS
WORKS. THERE MAY HAVE TO BE ECHOED A 1 AFTER echo a FOR SETTING BOOT FLAG
\begin{lstlisting}[]
<@\Suppressnumber @># (echo o;                                      # Create DOS partition table
    echo n; echo p; echo 1; echo ; echo +64M;   # Create boot partition
    echo t; echo b;                             # Set boot partition type to FAT
    echo a;                                     # Set boot flag
    echo n; echo p; echo 2; echo ; echo ;       # Create home partition
    echo w                                      # Write table to disk
    ) | sudo fdisk ${HTTPDEV} <@\Reactivatenumber @>
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

Mount the boot partition from the memory card. Copy the content from the
boot image and unmount it again:
\begin{lstlisting}[]
# mount ${HTTPDEV}p1 ${HTTPROOTDIR}/mnt
# cp -r ${HTTPROOTDIR}/boot/* ${HTTPROOTDIR}/mnt/ && sync
# umount ${HTTPROOTDIR}/mnt
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Mount the home partition from the memory card. Copy the content from the
root image and unmount it again:
\begin{lstlisting}[]
# mount ${HTTPDEV}p2 ${HTTPROOTDIR}/mnt
# cp -r ${HTTPROOTDIR}/home/* ${HTTPROOTDIR}/mnt/ && sync
# umount ${HTTPROOTDIR}/mnt
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\begin{lstlisting}[]
# umount --recursive ${HTTPROOTDIR}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\subsubsection{(Optional) Compressing root image}

PROBABLY A BETTER IDEA TO USE BTRFS TRANSPARENT COMPRESSION

\begin{lstlisting}[]
# apt-get install squashfs-tools
# mount -o loop ${HTTPROOTIMAGE}.img ${HTTPROOTDIR} 
# mksquashfs ${HTTPROOTDIR} compressed_${HTTPROOTIMAGE}.img       
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\subsubsection{Try it out}

Upload the root image (\$\{HTTPROOTIMAGE\}.img) to the HTTP server used in the
configurations above. Then, unplug the memory card from the computer.
Insert it into a \ac{Raspi} and
turn it on. It is recommended that the \ac{Raspi} is turned on with a monitor
connected the first time the newly created Linux installation is tested to
assure that Raspbian starts up correctly.

PRESENT FILES ON HTTP. E.G. HTTPROOT.IMG AND IMAGES.CSV
